\documentclass[letterpaper,10 pt]{article}
\usepackage{multicol}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome} % ← added for external link icon
\input{glyphtounicode}

% External link command
\newcommand{\externalLink}[2]{\href{#1}{#2\ \faExternalLink}}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom resume commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
\vspace{-35 pt}
\textbf{\Huge \scshape Sushil Kumar} \\ \vspace{1pt}
9875446168 $||$ sushil13129340@gmail.com $||$ 
\externalLink{https://www.linkedin.com/in/sushil1312/}{linkedin.com/in/sushil1312} $||$ \externalLink{https://github.com/SUSHIL1312}{github.com/sushil1312}
\end{center}

\vspace{-20 pt}



\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages:} C/C++, C\#, Python  \\
\textbf{Databases:} MySQL, SQL, Redis \\
\textbf{Platforms:} Android, Linux  \\
\textbf{Concepts:} OOP, Data Structure \& Algorithms, System Design, Operating System, Multithreading, IPC, Microservices, REST APIs, DBMS, Machine Learning, Deep Learning, LLMs, Generative AI, PyTorch  \\
\textbf{DevOps/Tools:} Kafka, RabbitMQ, Git, GitHub, CI/CD, AWS, Jira, TeraTerm, Visual Studio, Confluence \\
\textbf{Soft Skills:} Leadership, Innovation, Teamwork, Effective Communication, Root-Cause Analysis, Data-Driven Decision-Making \\
\vspace{2pt}
\textbf{Professional Summary:} Software Engineer with \textbf{$\sim$4 years of experience} in full-cycle development, system debugging, and rapid POC delivery. Experienced in leading teams, mentoring interns, and collaborating cross-functionally to build scalable, high-impact software solutions.
}}
\end{itemize}


\vspace{-20pt}
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Samsung R\&D Institute, Delhi - Software Engineer }{July 2022 - Present}
{}{}
\vspace{-18pt}
\resumeItemListStart

\resumeItem{\textbf{SmartMirror App \externalLink{https://www.ces.tech/ces-innovation-awards/2025/micro-led-beauty-mirror/}{(CES 2025 Best of Innovation Award)}:} Engineered an AI-powered MICRO LED smart mirror—the world’s first mirror-display hybrid—enabling real-time user detection (within 1 meter), advanced skin analysis, and personalized treatment recommendations.}

\resumeItem{Implemented computer vision pipelines using object detection (DeviceCare, sub-70ms), image segmentation (sunscreen analysis, sub-150ms), and MediaPipe for face detection and tracking (sub-50ms), achieving real-time performance on-device.}

\resumeItem{Integrated camera streaming, voice interaction, and LLM-based capabilities to deliver personalized insights on health (blood pressure, mental wellness), daily schedule, and product recommendations. Built on Linux and Android platforms.  \textit{[C++, C\#, Python]}}

\resumeItem{\textbf{POCs for Skin Health:} Led development of on-device \textbf{DeepLabV3+} with MobileNetV3 backbone for multi-class segmentation of acne, wrinkles, and pores, enabling real-time pixel-level visual overlays with sub-120ms inference latency.}

\resumeItem{Trained using a combination of public dermatology datasets ( Dermnet, ACNE04 ) and custom annotated data, achieving ~70\% mean IoU on a held-out test set and optimized inference latency using INT8 quantization. \hfill \textit{[Python, OpenCV]}}

\resumeItem{\textbf{The Player App:} Developed an intelligent portable media player (POC) for CES that detects nearby users and estimates relative distance to optimize multimedia experiences. Designed real-time master-client synchronization using WebSockets with timestamp alignment and drift correction, ensuring low-latency, near-synchronous playback across multiple devices. Integrated LLM capabilities to enhance interactive media experiences. \hfill \textit{[C++, C\#]}}
\resumeItem{\textbf{360 Degree audio support in Samsung Galaxy earbuds:} Contributed to the development of 360 degree immersive audio support with head tracking for Samsung Galaxy earbuds, enhancing the video and music experience. [C++, BLE]}

\resumeItem{\textbf{Enhanced Audio and Visual experience in Samsung TV:} Enhanced audio-visual preferences for sports, movie, and general modes using MVC architecture, resulting in a 20\% increase in user satisfaction.}

\resumeItem{\textbf{SmartAV Daemon:}Re-architected legacy C++ modules into a C++ \& C\# hybrid system with a daemon service to manage AV experiences on Samsung TV. Leveraged SOLID principles and integrated 150+ APIs to boost performance by 20\% and reduce bugs by 25\%.Improved IPC via D-Bus, achieving a SAM score of 4.85. [C++, C\#]}

\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}
\section{Publications}
\resumeSubHeadingListStart
\resumeSubheading
{Resolving Semantic Confusions for Improved Zero-Shot Detection}{BMVC-2022}
{Published: Nov 24, 2022}{\externalLink{https://bmvc2022.mpi-inf.mpg.de/0347.pdf}{Paper link}}
\resumeItemListStart
\resumeItem{Proposed a novel zero-shot object detection framework using Faster-RCNN trained on limited classes. Leveraged a Conditional WGAN to generate synthetic visual features from word vectors, addressing semantic confusion through triplet and cyclic-consistency loss. Achieved an 8\% relative mAP gain over the next-best method for detecting unseen objects on MSCOCO.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-16pt}
\section{Education}
2020--2022: \textbf{M.Tech} (Computer Science), \textbf{IIT Guwahati} \hfill (CGPA: 8.71)\\
2015--2019: \textbf{B.Tech} (Computer Science), \textbf{IIIT Kalyani} \hfill (CGPA: 8.21)\\

\vspace{-10pt}
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
{Banking System}{\externalLink{https://github.com/SUSHIL1312/Banking_System}{GitHub}}
{}{}
\vspace{-15pt}
\resumeItemListStart
\resumeItem{Built a banking system using C++ and TCP socket programming, supporting 50+ concurrent clients by designing a multithreaded client-server architecture for efficient request processing and communication.}\resumeItemListEnd



\resumeSubHeadingListEnd

\vspace{-10pt}
\section{Achievements \& Extracurricular Activities}
\resumeSubHeadingListStart

\resumeItemListStart
\resumeItem{Secured \textbf{AIR 387} among 100K candidates who appeared in \textbf{GATE 2020 }examination.}
\resumeItem{Solved over \textbf{800 coding problems} on platforms: 
\externalLink{https://leetcode.com/u/dark_knight9340/}{LeetCode}, 
\externalLink{https://www.interviewbit.com/profile/sushil1312/}{InterviewBit}, 
\externalLink{https://www.geeksforgeeks.org/user/sushil90350/}{GFG}.}

\resumeItem{Awarded Best Code Review in 2024 for writing high-quality, efficient, scalable, and clean code at SRID.}

\resumeItem{\textbf{Spot Award (2023; twice in 2025)} at SRI-Delhi for exceptional contributions to project delivery and team impact.}


\resumeItem{Completed NPTEL Online Certification in Algorithm and Analysis with a 97\% score.}
\resumeItem{\textbf{Teaching Assistant }for Computing Lab (CS 110), Machine Learning \& Deep Learning (CS 590) course at IIT Guwahati.}




\resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
